A thesis draft

### 2018-10-25 res/sections/10-ProjectAnalysis.tex
Add about Harbor

\subsubsection{Harbor} \todo{Talk about harbor!}
Started as a Virtual VNFM (Network Function Virtualization Manager) for 
Openbaton, during the project it has been expanded to become a complete 
replacement of the original product, adding the possibility to manage Network 
Services and to update the route tables, Roulette Controller (the tool 
description can be found in \todo{Insert roulette ref!}).

>>>>

\subsubsection{Harbor}
Started as a Virtual VNFM (Network Function Virtualization Manager) to offer 
a bridge for Openbaton to interact with Kubernetes, during the project it has 
been expanded to become a complete replacement of the original product, adding 
the possibility to manage Network Services and to update the route tables, 
Roulette Controller (the tool description can be found below
in~\ref{chap:prjan:sec:tech:sub:SFC:sub:roulette}). Harbor doesn't have a web 
interface, but it has a RESTful API that can allow users to interact with him 
using CRUD operations.

\subsection{SFC}

\subsubsection{Roulette Controller}
\label{chap:prjan:sec:Stech:sub:SFC:sub:roulette}

\subsubsection{Astaire}

\subsubsection{Ironhide}
